Icicle: a single-pass query language

### 2015-11-14 2016icicle/section/01-Introduction.tex
ok

>>>>

For feature generation for machine learning, our queries have some quite specific restrictions.
Queries only need to read from one `table', for example the stocks table with company codes, dates and open and close prices for each day.
Each query is implicitly partitioned by the entity, the company code in this case, and performs an aggregate over that company's entries, sorted by date.
In this way, our query language is actually a streaming dataflow language with only one input stream and clock.
By making use of these restrictions, we are able to generate more efficient code than a general query language.

### 2015-11-14 2016icicle/section/02-Source.tex
ok

We can also use @group@ to put into buckets based on the percentage of growth.
Here the key for the map is the percentage of growth, and the value is the number of days with that amount of growth, divided by the total number of days.
\begin{code}
growthPercent
 =  int ((close - open) / open * 100)

@@

Finally, we could compare the average growth over the last five entries to the average growth over the last fifty entries, and see which is bigger.
\begin{code}
compareGrowth
 =  (latest 5  ~> mean growthPercent)
 -  (latest 50 ~> mean growthPercent)

\end{code}

>>>>

Finally, we can use @group@ to put into buckets based on the percentage of growth.
Here the key for the map is the percentage of growth, and the value is the number of days with that amount of growth, divided by the total number of days.
\begin{code}
growthPercent
 =  int ((close - open) / open * 100)

@@

\TODO{Mention resumables and bubblegum?}
